A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-29 paper.tex
Work in progress
Background check
Work in progress
Description and Background update

\section{Description of the sections of the Paper}

\section{State of the art}

Multiple citations are grouped \cite{valdez2021container,krejca2020lower,witt2019upper,merelo2016nodio,merelo2016performance,fortin2012deap,stanley2002evolving}.

% For citations of references, we prefer the use of square brackets
% and consecutive numbers. Citations using labels or the author/year
% convention are also acceptable. The following bibliography provides
% a sample reference list with entries for journal
% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
% and a homepage~\cite{ref_url1}. Multiple citations are grouped
% \cite{ref_article1,ref_lncs1,ref_book1},
% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.

\subsection{Background}

One of the publications with the most influence on our research proposes a
cloud-native optimization framework, that can include multiple
(population-based) algorithms~\cite{valdez2021container}. In their research, they work with ideas such
as those mentioned in Fig.~\ref{fig1}.

>>>>

\section{Description} 
% Description of the sections of the Paper
% We structure this research paper as follows

We present the description of the following sections in our research paper.

\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
    \item[$\cdot Background$] We do a brief explanation of our motivation for this research.
    \item[$\cdot Proposal$] We present an algorithm inspired by the Life-Cycle of animal species.
    \item[$\cdot Experiments$] We specify our experimental setup, configuration, and results.
    \item[$\cdot Discussion$] We analyze and describe some of our research findings.
    \item[$\cdot Conclusions$] We present some inferences based on our experiments' results.
    \item[$\cdot References$] We enumerate the references for our research paper.
\end{description}

\section{Background}

% For citations of references, we prefer the use of square brackets
% and consecutive numbers. Citations using labels or the author/year
% convention are also acceptable. The following bibliography provides
% a sample reference list with entries for journal
% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
% and a homepage~\cite{ref_url1}. Multiple citations are grouped
% \cite{ref_article1,ref_lncs1,ref_book1},
% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
% Multiple citations are grouped \cite{valdez2021container,krejca2020lower,witt2019upper,merelo2016nodio,merelo2016performance,fortin2012deap,stanley2002evolving}.

One of the publications with the most influence on our research proposes a
cloud-native optimization framework, that can include multiple
(population-based) algorithms~\cite{valdez2021container}. In their research,
they work with ideas such as those mentioned in Figure~\ref{fig1}.
